### 2020-06-04 writeup/intro.tex
abstract

\begin{abstract}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach to solve complex tasks in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	In this work, we study this question formally by considering three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} in the setting of high-dimensional linear regression.
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	First, we show that whether multi-task learning performs better than single-task learning is determined by the bias-variance tradeoff of multi-task estimators.
	We analyze the bias-variance tradeoff by developing technical tools using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Second, we apply our tools to show that the performance of multi-task learning is negatively affected as a result of: (a) decreased task similarity;
	(b) increased source sample size; (c) covariate shift under increased source sample size.
	Finally, we validate the three components of our theory on image and text classification tasks.
	Inspired by our theory, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

>>>>

\begin{abstract}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach to solve complex tasks in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	In this work, we study this question by considering three components including \textit{task model distance}, \textit{sample size} and \textit{covariate shift} in the setting of high-dimensional linear regression.
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	We show that whether multi-task learning performs better than single-task learning is determined by the bias-variance tradeoff of the multi-task estimator.
	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Then, we show that the performance of multi-task learning can be negatively affected as a result of: (a) increased task model distance;
	(b) increased source sample size; (c) covariate shift under increased source sample size.
	Finally, we validate the above results on text classification tasks.
	Inspired by our theory, we show that single-task performance can help understand multi-task performance. We propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

### 2020-06-04 writeup/setup.tex
abstract

We begin by defining our problem setup including the multi-task estimator we study.
Then, we describe the bias-variance tradeoff of the multi-task estimator, and connect the bias and variance of the estimator to \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.

>>>>

We begin by defining our problem setup including the multi-task estimator we study.
Then, we describe the bias-variance tradeoff of the multi-task estimator, and connect the bias and variance of the estimator to \textit{task model distance}, \textit{sample size} and \textit{covariate shift}.
%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.

### 2020-06-04 writeup/transfer.tex
abstract

%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
We show theoretical implications for understanding the performance of multi-task learning.
(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as task models become different.
(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
(c) \textit{Covariate shift}: as source sample size increases, we show that covariate shift worsens the performance of the multi-task estimator.
Finally, we extend our result from two tasks to many tasks with the same features.
%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
%We show how negative transfer occurs by varying task similarity or sample size.
%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.

@@

For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task similarity in addition to sample size and covariate shift holds (cf. Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).

@@

\subsection{Task Similarity}\label{sec_similarity}

>>>>

%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
We show theoretical implications for understanding the performance of multi-task learning.
(a) \textit{Task model distance}: we explain the phenomenon of negative transfer precisely as task models become different.
(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
(c) \textit{Covariate shift}: as source sample size increases, we show that covariate shift worsens the performance of the multi-task estimator.
Finally, we extend our result from two tasks to many tasks with the same features.
%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
%We show how negative transfer occurs by varying task similarity or sample size.
%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.

@@

For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task model distance in addition to sample size and covariate shift holds (cf. Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).

@@

\subsection{Task Model Distance}\label{sec_similarity}
